mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-07 Draft2.Rmd
add mistakes

mathout <- function(term)
{
  if(knitr::is_html_output())
    return(mathml(term))

  if(knitr::is_latex_output())
    return(mathjax(term))

  warning("no output specified")  
  mathjax(term)
}

catmath <- function(term)
{
  s <- substitute(term)
  mathout(canonical(s))
}
```

@@

```{r, results='asis', echo=TRUE}
catmath(x^y + z)

@@

>>>>

mathout <- function(...)
{
  if(knitr::is_html_output())
    return(mathml(...))

  if(knitr::is_latex_output())
    return(mathjax(...))

  warning("no output specified")  
  mathjax(...)
}

catmath <- function(term, ...)
{
  s <- substitute(term)
  mathout(canonical(s), ...)
}
```

@@

```{r, results='asis', echo=TRUE}
first <- quote(a)
second <- quote(b + c)
mathout(call("*", first, second))

catmath(x^y + z)
mathout(call("+", call("^", as.symbol("x"), as.symbol("y")), as.symbol("z")))

@@

```{r, results="asis"}
t <- quote(omit_left(a + b))
mathout(t)
```

```{r, results="asis"}
t <- quote(omit_right(a + b))
mathout(t)
```

```{r, results="asis"}
t <- list(quote(a), quote(b), quote(omit(c)))
mathout(t)
```

```{r, results="asis"}
t <- quote(add_left(a + b))
mathout(t)
```

```{r, results="asis"}
t <- quote(add_right(a + b))
mathout(t)
```

```{r, results="asis"}
t <- list(quote(a), quote(b), quote(add(c)), quote(d))
mathout(t)
```

```{r, results="asis"}
t <- quote(instead(a, b) + c)
mathout(t)
```

also mention the use of these flags for context-dependent rendering

```{r, results="asis"}
t <- quote(omit_left(a + b))
mathout(t, flags=quote(error(highlight))) # default
```

```{r, results="asis"}
mathout(t, flags=quote(error(ignore)))
```

```{r, results="asis"}
mathout(t, flags=quote(error(fix)))
```
